Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA

### 2021-07-21 paper/tex/sections/results.tex
update galaxy plot and remove old one

In the lower panel of Fig.~\ref{fig:detectable_distance_dist}, we show the density distribution for detectable DCOs in the galaxy. We see that most sources are concentrated in the Galactic center, with a bias towards to the position of the Sun. Yet we also show that systems are detectable out to the edges of the galaxy and this is especially true for NSNSs.

\begin{figure}[thb]
    \centering
    \includegraphics[width=\columnwidth]{detectable_distance_distribution_4yr.pdf}
    \includegraphics[width=\columnwidth]{galaxy_density_distribution.png}
    \caption{\textbf{Top:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance. \textbf{Bottom:} A face-on view of the Galactic density distribution for detectable DCOs. We only show the density distribution for the top 95\% of the sources, the rest are indicated by scatter points whose sizes correspond to their STROOPWAFEL weights. The coloured lines show the 90\% contour for each of the individual DCO types. The `x' shows the centre of the galaxy, whilst the $\odot$ shows the position of the Sun.}
    \label{fig:detectable_distance_dist}
\end{figure}

>>>>

In the lower panel of Fig.~\ref{fig:detectable_distance_dist}, we show the density distribution for detectable DCOs in the galaxy. We see that most sources are concentrated in the Galactic center, with a bias towards to the position of the Sun. Yet we also show that systems are detectable out to the edges of the galaxy. This is especially true for NSNSs, as we highlight by plotting the 75\% contour for the individual DCO types.

\begin{figure}[thb]
    \centering
    \includegraphics[width=\columnwidth]{detectable_distance_distribution_4yr.pdf}
    \includegraphics[width=\columnwidth]{galaxy_density_distribution.png}
    \caption{\textbf{Top:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance. \textbf{Bottom:} A face-on view of the Galactic density distribution for detectable DCOs. We only show the density distribution for the top 95\% of the sources, the rest are indicated by scatter points whose sizes correspond to their STROOPWAFEL weights. The coloured lines show the 75\% contour for each of the individual DCO types. The $\odot$ shows the position of the Sun.}
    \label{fig:detectable_distance_dist}
\end{figure}
